Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2021-02-23 summary.Rmd
minor tweaks

```{r}
dplyr::tibble(Network = c('British MPs', 'Political blogs', 'DBLP'),
              Vertices = c(nrow(A.bmp), nrow(A.pb), nrow(A.dblp)),
              `Error (Mod. Max.)` = c(round(1 / 329, 3),
                                      round(61 / 1222, 3),
                                      round(62 / 2203, 3)),
              `Error (SSC)` = round(1 - c(bmp.acc.ssc,
                                          pb.acc.ssc,
                                          dblp.acc.ssc), 3),
              `Error (OSC)` = round(1 - c(bmp.acc, 
                                                  pb.acc,
                                                  dblp.acc), 3)) %>% 
  knitr::kable(caption = paste('Community detection error rates', 
                               'for modularity maximization,',
                               'sparse subspace clustering, ',
                               'and OSC.'))
```

@@

A.hh.46 <- hh.46$A
z.hh.46 <- hh.46$z
zhat.hh.46 <- cluster.pabm(A.hh.46, K,
                           use.all = TRUE, normalize = FALSE, p = 2, q = 0)
zhat.hh.ssc.46 <- ssc(A.hh.46, K, lambda = .0005)
zhat.hh.mm.46 <- mm(A.hh.46)

@@

knitr::kable(dplyr::tibble(
  Method = c('OSC', 'SSC', 'Mod. Max.'),
  `Error (Village 12)` = round(1 - c(hh.acc.12, hh.acc.ssc.12, hh.acc.mm.12), 3),
  `Error (Village 31)` = round(1 - c(hh.acc.31, hh.acc.ssc.31, hh.acc.mm.31), 3),
  `Error (Village 46)` = round(1 - c(hh.acc.46, hh.acc.ssc.46, hh.acc.mm.46), 3)),
  caption = paste('Community detection error rates for identifying',
                  'household religion.'))
```

>>>>

```{r}
dplyr::tibble(Network = c('British MPs', 'Political blogs', 'DBLP'),
              # Vertices = c(nrow(A.bmp), nrow(A.pb), nrow(A.dblp)),
              `MM` = c(round(1 / 329, 3),
                       round(61 / 1222, 3),
                       round(62 / 2203, 3)),
              `SSC-ASE` = round(1 - c(bmp.acc.ssc,
                                      pb.acc.ssc,
                                      dblp.acc.ssc), 3),
              `OSC` = round(1 - c(bmp.acc, 
                                  pb.acc,
                                  dblp.acc), 3)) %>% 
  knitr::kable(caption = paste('Community detection error rates', 
                               'for modularity maximization,',
                               'sparse subspace clustering, ',
                               'and OSC.'))
```

@@

A.hh.46 <- hh.46$A
z.hh.46 <- hh.46$z
zhat.hh.46 <- cluster.pabm(A.hh.46, K,
                           use.all = TRUE, normalize = FALSE, p = 2, q = 0)
zhat.hh.ssc.46 <- ssc(A.hh.46, K, lambda = .001)
zhat.hh.mm.46 <- mm(A.hh.46)

@@

# knitr::kable(dplyr::tibble(
#   Method = c('OSC', 'SSC-ASE', 'Mod. Max.'),
#   `Village 12` = round(1 - c(hh.acc.12, hh.acc.ssc.12, hh.acc.mm.12), 3),
#   `Village 31` = round(1 - c(hh.acc.31, hh.acc.ssc.31, hh.acc.mm.31), 3),
#   `Village 46` = round(1 - c(hh.acc.46, hh.acc.ssc.46, hh.acc.mm.46), 3)),
#   caption = paste('Community detection error rates for identifying',
#                   'household religion.'))

knitr::kable(dplyr::tibble(
  Network = c('Village 12', 'Village 31', 'Village 46'),
  MM = round(1 - c(hh.acc.mm.12, hh.acc.mm.31, hh.acc.mm.46), 3),
  `SSC-ASE` = round(1 - c(hh.acc.ssc.12, hh.acc.ssc.31, hh.acc.ssc.46), 3),
  `OSC` = round(1 - c(hh.acc.12, hh.acc.31, hh.acc.46), 3)
),
caption = paste('Community detection error rates for identifying',
                  'household religion.'))
```
